Active Learning from Blackbox to Timed Connectors

### 2016-01-19 paper/paper.tex
.

\section{From Blackbox to Timed Connectors} 
\label{sec:activelearning}
In this section, we show how to use L* algorithm to extract models from blackboxes in  3 steps:
\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{checking hypothesis}. Besides,
we assume that input symbols and output symbols of the blackbox have been provided as $\mathcal{I}$
and $\mathcal{O}$.

\subsection{Observation Table}
As mentioned above, membership queries provide us information with the form $mq(s)=o$, where $s$ is
an input sequence in $\Sigma^{+}$. Now the question is, \emph{how to find the connection between
such query results and Mealy machines?}

@@

Different access sequences may lead to similar states. For example, a 2-Timer channel will dispense
any accepted data item in 2 time units. After that, the state of this channel is exactly same as its
initial state. Here \emph{suffixes} are used to distinguish different states as shown in the
following definition, where $D$ is initialized as $\mathcal{I}$. Under such a suffix set, two states
are considered different only when they have different one-step behaviors.

\begin{definition}[Equivalence under Suffixes]
  provided with two access sequences $s_1,s_2$ and a set of suffixes $D\subset\mathcal{I}^+$, we say
  the corresponding states of $s_1$ and $s_2$ are equivalent under $D$ (denoted as $s_1\sim_D s_2$)
  iff $\forall d\in D, mq(s_1d) = mq(s_2d)$.
\end{definition}

>>>>

\section{From Blackbox to Timed Connectors} 
\label{sec:activelearning}
In this section, we use L* algorithm to extract Reo coordinators from blackbox
implementations in 3 steps:
\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. Besides,
Here the input symbols and output symbols of the blackbox are supposed to be provided as $\mathcal{I}$
and $\mathcal{O}$.

\subsection{Observation Table}
Results of membership queries come out as $mq(s)=o$, where $s\in\mathcal{I}+$.
Now the question is, \emph{how to find the connection betweensuch query results and Mealy machines?}

@@

Different access sequences may lead to similar states. Here we use \emph{suffixes} set $D$ to
distinguish states where $D\subseteq \mathcal{I}^+$ is initialized as $\{d=\{i\}|i\in\mathcal{I}\}$. 
\begin{definition}[Equivalence under Suffixes]
  provided with two access sequences $s_1,s_2$ and a set of suffixes $D\subset\mathcal{I}^+$, we say
  the corresponding states of $s_1$ and $s_2$ are equivalent under $D$ (denoted as $s_1\sim_D s_2$)
  iff $\forall d\in D, mq(s_1d) = mq(s_2d)$.
\end{definition}
